---
title: "Replication of Study by Nekmat et al. (2015, Communication Research)"
author: "Mufan Luo (mufanl@stanford.edu)"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
---

<!-- Replication reports should all use this template to standardize reporting across projects.  These reports will be public supplementary materials that accompany the summary report(s) of the aggregate results. -->

##Introduction

The main goal of the original study was to examine the effects of personal sources of online messages on individuals' willingness to engage in connective-type collective activities on social media. It also investigated whether this causal relationship was moderated by perceived credibility, and mediated by cognitive elaboration. This replication project focused on the main effect of the information source on online participation, and the moderating role of perceived credibility. 

##Methods

The original study was an online experiment manipulating message source (i.e., close personal source vs. impersonal organizational source). The experiment consisted of a pretest which involved all control variables and a posttest including dependent variables and metiating and moderating variables conducted a weak after.

###Power Analysis

As reported in the method section of the original paper, the original effect size of the main effect ($N = 208$) was $f^2 = .394$ ($F (5, 207)$ = 15.98,$p <.001$). Accordingly, GPower was used to calculate the posthoc power which almost achieved 1.0. Building off of it, I did a priori analysis in GPower, setting the test family as $F$ test, and $\alpha$ probability as .05. Three different sample sizes were obtained depending on different power. In particular, 95% power required in total 58 participants. 90% power led to $N = 49$ sample size, whereas 80% power led to $N = 40$. I decided to recruit 58 participants in this replication project, since the corresponding power was cloest to the posthoc power of the original study. Note: Screenshots of all power analysis are accessible through Open Science Framework (will add after pre-registering).

###Planned Sample

Following the original study, this replication work recruited undergraduates enrolled in Psychology and Communication courses at Stanford University who participated this study for extra credit. Therefore, this sample would be very similar to the original study with regards to age and gender (only age and gender were reported in the original study). 

###Materials

Materials of the experimental stimuli were critical in this replication project. Here, both instructions and message stimuli were discussed in details. 
First, with respect to message stimuli, the original study created an online post that read *"The University is removing the Quad[central park] to build classrooms and offices. The group Students for Nature is campaigning against this. Please support."*
Second, participants read the instructions that said, *"You have received this message from [specific source variable tested] on one of your social media accounts(e.g., Twitter, Facebook, etc.)."* In addition, following the same instructions of the original study, participants were either told that the message had come from *"(1)a member of their close personal network (i.e., someone to whom you are very close). The person might be a family member, friend, classmate, or anyone else you know personally; or (2) an organizational source (i.e., an official from the group Students for Nature)"*.

###Procedure	
The experiment can be found here: [Nekmat Replication](https://stanforduniversity.qualtrics.com/jfe/form/SV_9HtwvJqPfeBajUV)
In this replication study, participants signed the consent form and entered the above survey. They were randomly assigned to two conditions (a personal source vs. an organizational source), reading the same message but different instructions (see the Material section). In particular, following the original study, *"participants who received the message from a close personal source were asked to write on the questionnaire the name of a person to whom they were close and connected to via social media"*. After reading the online post, participants answered questions regarding a manipulation check, dependent variables, moderating (i.e., perceived credibility) and mediating (i.e., cognitive elaboration) variables, four control variables (personal issue involvement, attitude toward activism, perceived efficacy), and demographic information in the original study. 

###Analysis Plan
First, hierarchical regression analysis is needed to test the effect of information source on online participation (H1). In addition, MANCOVA will be applied to investigate the effect of information source on individuals' willingness to engage in different types of connective-collective activities (R1). Last, multivariate regression analysis is needed to examine the moderating role of perceived source credibility on willingness of online participation (H3) and cognitive elaboration (H4). 

**Clarify key analysis of interest here** 
Key analysis includes a hierarchical regression analysis of H1*("when compared with messages passed by organizational sources, those passed by personally closer people (e.g., friends, family) would lead to greater willingness to participate in collective activities on social media)"* Results in the original study showed that blocking for control variables, personally closer sources were significantly more influential ($M = 5.44, SD = 1.21$) than organizational sources ($M = 4.02, SD = 1.41$), with $\Delta R^2 = .194, F(5, 207) = 15.98, p < .001, \beta = .44, f^2 = .394, R^2 = .27 (adjusted)$. Among the covariates, significant relationships were found for personal issue involvement ($\beta = .210, p < .001$) and perceived internal efficacy ($\beta = .208, p < .01$).

###Differences from Original Study

The current replication study is different from the original one from the following perspectives. 
The first and most noticalbe difference is the sample size: N = 208 (original study) vs. 58 (replication study). 
The second main difference is concerned with the study procedure. The pretest and posttest, in the original study, were conducted seperately at 7 days interval. The original paper argued that *"to reduce, if not remove, any systematic influences from participants' self-report of personal issue involvement attitude toward activism, and perceived efficacy, data on these predispositional factors were collected as the study's control variables in the first questionniare. Participants were then randomly assigned to one of two source scenarios in the second questionnaire administedred 7 days later"*. However, given the tight timeline, the current replication study combined two studies, measuring all control variables, dependent variables, mediator and moderator simultanesouly. I would argue that the systematic influences may not affect the final result significantly. 
Third, the experiment stimulus in the replication study was distinct from the original one, although both of them dealt with the same social issue---protecting the environment. To make the message stimulus more realistic and plausible to Stanford students, the online post used in the replication study read "The University plans to open offices and build classrooms in the area surrounding the Dish. The group Students for Sustainable Stanford is campaigning against this." The modification of the message stimuli is both necessary and important, due to the different college sample of Stanford undergraduates. 

### Methods Addendum (Post Data Collection)

You can comment this section out prior to final report with data collection.

#### Actual Sample
  Sample size, demographics, data exclusions based on rules spelled out in analysis plan

#### Differences from pre-data collection methods plan
  None. 


##Results


### Data preparation

Data preparation following the analysis plan.
	
```{r include=F}
####Load Relevant Libraries and Functions
library(psy)
library(psych)
library(tidyverse)
library(MANOVA.RM)
library(ggplot2)
####Import data
data <- read.csv(file = "/Users/mufanluo/psych251/Nekmat2015/pilota_cleaned.csv", header = TRUE)
head(data)
#### Prepare data for analysis - create columns etc.
attach(data)
## manipulation check
check <- cbind(M1, M2, M3)
cronbach(check)
newd <- data%>%
  mutate(manipulation = apply(check, 1, mean))
## perceived credibility (moderator) 
cred <- cbind(credible_1, credible_2, credible_3, credible_4, credible_5)
cronbach(cred)
newd <- newd%>%
  mutate(credibility = apply(cred, 1, mean))
##online action (dependent variable)
act<- cbind(action_1, action_2, action_3, action_4, action_5, action_6, action_7, action_8)
cronbach(act)
newd <- newd%>%
  mutate(action = apply(act, 1, mean))
##cognitive elaboration (mediator)
ce <- cbind(CE_1, CE_2)
cronbach(ce)
newd <- newd%>%
  mutate(elaboration = apply(ce, 1, mean))
##involvement (control)
inv <- cbind(INV_1, INV_2, INV_3, INV_4)
cronbach(inv)
newd <- newd%>%
  mutate(involvement = apply(inv, 1, mean))
##attitude (control)
att <- cbind(ATT_1, ATT_2, ATT_3, ATT_4, ATT_5)
cronbach(att)
newd <- newd%>%
  mutate(attitude = apply(att, 1, mean))
##percevied self-efficacy (control)
eff1 <- cbind(EFF_1_1, EFF_1_2)
cronbach(eff1)
newd <- newd%>%
  mutate(efficacy = apply(eff1, 1, mean))
##internet efficacy (control)
eff <- cbind(EFF_1_3, EFF_1_4)
cronbach(eff)
newd <- newd%>%
  mutate(tech_efficacy = apply(eff, 1, mean))
eff <- cbind(EFF_1_1, EFF_1_2, EFF_1_3, EFF_1_4)
cronbach(eff)
##group efficacy (control)
group <- cbind(EFF_2_1, EFF_2_2, EFF_2_3, EFF_2_4, EFF_2_5)
cronbach(group)
newd <- newd%>%
  mutate(internal = apply(eff, 1, mean))
newd <- newd%>%
  mutate(group_eff = apply(group, 1, mean))
newd2 <- newd[c(1:2, 39:50, 11:17)]

##Descriptives of key variables
describe(newd2[, 3:21])
```

### Confirmatory analysis

First, Manipulation check of experimental treatment: personal-ness of information source.
```{r, message=FALSE}
source <- as.factor(Source)
check <- lm (manipulation ~ source, data = newd2)
summary(check)
personal <- newd2%>%
  filter(Source =="personal")
impersonal <- newd2%>%
  filter(Source =="impersonal")
mean(personal$manipulation)
mean(impersonal$manipulation)
sd(personal$manipulation)
sd(impersonal$manipulation)
```
Second, key analysis of H1: Receiving messages directly from personal sources (i.e., family,friends) as compared with impersonal sources (i.e., organizational source) will lead to greater willingness to participate in connective-collective activities on social.
media.
```{r, message=FALSE}
attach(newd2)
##hiearachical linear regression
lm1 <- lm(action ~ source)
lm2 <- lm(action ~ source + attitude + involvement + internal + group_eff)
lm3 <- lm(action ~ attitude + involvement + internal + group_eff)
summary(lm1)
summary(lm2)
summary(lm3)
##Using anova to compare models to examine if controling for 4 variables could improve the model fit.
anova(lm1, lm2, lm3)
```

*Figure 1*
Using barplot to visualize the main effect of personal-ness of online participation. 
```{r}
ggplot(data=newd2, aes(x= source, y=action)) +
  geom_bar(stat="identity")
```

###Exploratory analyses

In addition to the key analysis, this replication project also investigated R1, H3 and H4 in the original study. 

RQ1: Are there significant differences between personal and impersonal sources in influencing individuals’ willingness to engage in the different types of connective-collective activities?
```{r}
mod1 <-manova(act ~ source + attitude + involvement + internal + group_eff, data = newd2)
summary(mod1)
mod2 <- manova(act ~ source + elaboration, data = newd2)
#summary(mod2)
```

H3: Predicted that perceived source credibility will moderate source effects by being positively related to willingness to carry out the collective activities.
```{r}
mod3 <- lm(action ~ source*credibility)
summary(mod3)
```

H4: Perceived source credibility will moderate the influence of
personalness of source on cognitive elaboration, such that perceived credibility is positively related to cognitive elaboration.
```{r}
mod4 <- lm(elaboration ~ source*credibility)
summary(mod4)
```

Finally, try to replicate the interaction plots in the original study. 
```{r}
qplot(x = credibility, y = action, data = newd2, color = source) + 
  geom_smooth(method = "lm")
qplot(x = credibility, y = elaboration, data = newd2, color = source)+
  geom_smooth(method = "lm")
```


## Discussion

### Summary of Replication Attempt

Open the discussion section with a paragraph summarizing the primary result from the confirmatory analysis and the assessment of whether it replicated, partially replicated, or failed to replicate the original result.  

### Commentary

Add open-ended commentary (if any) reflecting (a) insights from follow-up exploratory analysis, (b) assessment of the meaning of the replication (or not) - e.g., for a failure to replicate, are the differences between original and present study ones that definitely, plausibly, or are unlikely to have been moderators of the result, and (c) discussion of any objections or challenges raised by the current and original authors about the replication attempt.  None of these need to be long.
