---
title: "Replication of Study by Nekmat and colleagues (2015, Communication Research)"
author: "Mufan Luo (mufanl@stanford.edu)"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
---

<!-- Replication reports should all use this template to standardize reporting across projects.  These reports will be public supplementary materials that accompany the summary report(s) of the aggregate results. -->

##Introduction

The main goal of the original study was to examine the effects of personal sources of online messages on individuals' willingness to engage in connective-type collective activities on social media. It also investigated whether this causal relationship was moderated by perceived credibility, and mediated by cognitive elaboration. This replication project focused on the main effect of the information source on online participation, and the moderating role of perceived credibility. 

##Methods

The original study was an online experiment manipulating message source (i.e., close personal source vs. impersonal organizational source). The experiment consisted of a pretest which involved all control variables and a posttest including dependent variables, a moderator, and a mediator conducted a weak after.

###Power Analysis

Original effect size of the main effect ($N$ = 202) was $f^2$ = .394. Therefore, in a priori analysis, I set the test family as f test, $\alpha$ probability as .05, and the power as .95, the final sample size of this replication project was 58. This sample size is feasible given the timeline.

###Planned Sample

Following the original study, this replication work recruited undergraduates enrolled in Psychology and Communication courses at Stanford University who participated the study for extra credit. This sample would be very similar to the original study with regards to age and gender (only age and gender were reported in the original study). 

###Materials

Following the original study, "two scenarios in the experiment consited of the same message by a fictional student environmental activist group on campus that read, 'The University is removing the Quad [central
park] to build classrooms and offices. The group Students for Nature is campaigning against this. Please support.'Participants were given instructions that said, 'You have received this message from [specific source variable tested] on one of your social media accounts (e.g., Twitter, Facebook, etc.).' All messages were less than 140 characters,
and so could plausibly appear in any popular social media platform."
Again, following the same instructions, participants were either told that the message had come from (1) a member of their close personal network (i.e., “someone to whom you are very close. The person might
be a family member, friend, classmate, or anyone else you know personally”; or (2) an organizational source (i.e., “an official from the group Students for Nature”).

###Procedure	
The experiment can be found here: [Nekmat Replication](https://stanforduniversity.qualtrics.com/jfe/form/SV_9HtwvJqPfeBajUV)
"Participants who received the message from a close personal
source were asked to write on the questionnaire the name of a person to whom they were close and connected to via social media, so as to create a more “personalized” and realistic scenario." After reading the post, participants answered questions regarding a manipulation check, dependent variables, a moderator (i.e., perceived credibility) and a mediator (i.e., cognitive elaboration) in the original study. 

###Analysis Plan
Hierarchical regression analysis is needed to test the effect of information source on online participation (H1 main effect). MANCOVA will be applied to investigate the effect of information source on individuals' willingness to engage in different types of connective-collective activities (R1).Multivariate regression analysis is needed for both H3 and H4 in the original study, the moderating role of perceived source credibility on willingness of online participation and cognitive elaboration. 

**Clarify key analysis of interest here** 
Key analysis includes a hierarchical regression analysis of the main effect.

###Differences from Original Study

With respect to the sample size, the original study recruited 208 undergraduates whereas the current replication project involved 58 participants. A key difference lies in the procedure. The original study conducted two studies, including pretest and posttest. Specifically, "to reduce, if not remove, any systematic influences from participants' self-report of personal issue involvement attitude toward activism, and perceived efficacy, data on these predispositional factors were collected as the study's control variables in the first questionniare. Participants were then randomly assigned to one of two source scenarios in the second questionnaire administedred 7 days later". Given the tight timeline, the current replication study combined two studies, measuring all control variables, dependent variables, mediator and moderator simultanesouly. Although the original study identified the reason to conduct a pretest a weak earlier than the main experiment, the systematic influences may not affect the final result significantly (cites). Third, the experiment stimulus in the replication study was distinct from the original one, although both of them dealt with the same social issue---protecting the environment. The original stimuli read "The University is removing the Quad to build classrooms and offices. The group Students for Nature is campaigning against this". To make the stimulus more realistic and plausible to Stanford students, the online post used in the replication study read "The University plans to open offices and build classrooms in the area surrounding the Dish. The group Students for Sustainable Stanford is campaigning against this." The modification of the message stimuli is both necessary and important, given the sample of Stanford students. 

### Methods Addendum (Post Data Collection)

You can comment this section out prior to final report with data collection.

#### Actual Sample
  Sample size, demographics, data exclusions based on rules spelled out in analysis plan

#### Differences from pre-data collection methods plan
  Any differences from what was described as the original plan, or “none”.


##Results


### Data preparation

Data preparation following the analysis plan.
	
```{r include=F}
####Load Relevant Libraries and Functions
library(psy)
library(tidyverse)
library(MANOVA.RM)
library(ggplot2)
####Import data
data <- read.csv(file = "/Users/mufanluo/psych251/Nekmat2015/pilota_cleaned.csv", header = TRUE)
head(data)
#### Prepare data for analysis - create columns etc.
attach(data)
## manipulation check
a <- cbind(M1, M2, M3)
cronbach(a)
newd <- data%>%
  mutate(manipulation = apply(a, 1, mean))
## perceived credibility 
b <- cbind(credible_1, credible_2, credible_3, credible_4, credible_5)
cronbach(b)
newd <- newd%>%
  mutate(credibility = apply(b, 1, mean))
##online action
c<- cbind(action_1, action_2, action_3, action_4, action_5, action_6, action_7, action_8)
cronbach(c)
newd <- newd%>%
  mutate(action = apply(c, 1, mean))
##cognitive elaboration
d <- cbind(CE_1, CE_2)
cronbach(d)
newd <- newd%>%
  mutate(elaboration = apply(d, 1, mean))
##involvement 
e <- cbind(INV_1, INV_2, INV_3, INV_4)
cronbach(e)
newd <- newd%>%
  mutate(involvement = apply(e, 1, mean))
##attitude
f <- cbind(ATT_1, ATT_2, ATT_3, ATT_4, ATT_5)
cronbach(f)
newd <- newd%>%
  mutate(attitude = apply(f, 1, mean))
##percevied self-efficacy 
g <- cbind(EFF_1_1, EFF_1_2)
cronbach(g)
newd <- newd%>%
  mutate(efficacy = apply(g, 1, mean))
##internet efficacy 
h <- cbind(EFF_1_3, EFF_1_4)
cronbach(h)
newd <- newd%>%
  mutate(tech_efficacy = apply(h, 1, mean))
j <- cbind(EFF_1_1, EFF_1_2, EFF_1_3, EFF_1_4)
cronbach(j)
##group efficacy
i <- cbind(EFF_2_1, EFF_2_2, EFF_2_3, EFF_2_4, EFF_2_5)
cronbach(i)
newd <- newd%>%
  mutate(internal = apply(j, 1, mean))
newd <- newd%>%
  mutate(group_eff = apply(i, 1, mean))
newd2 <- newd[c(1:2, 39:50, 11:17)]
```

### Confirmatory analysis

Manipulation check of personal-ness of information source
```{r, message=FALSE}
source <- as.factor(Source)
check <- lm (manipulation ~ source, data = newd2)
summary(check)
personal <- newd2%>%
  filter(Source =="personal")
impersonal <- newd2%>%
  filter(Source =="impersonal")
mean(personal$manipulation)
mean(impersonal$manipulation)
sd(personal$manipulation)
sd(impersonal$manipulation)
```

H1: Receiving messages directly from personal sources (i.e., family,
friends) as compared with impersonal sources (i.e., organizational source) will lead to greater willingness to participate in connective-collective activities on social
media.
```{r, message=FALSE}
attach(newd2)
lm1 <- lm(action ~ source)
qplot(x = source, y = action, data = newd2) + geom_smooth(method = "lm")
lm2 <- lm(action ~ source + attitude + involvement + internal + group_eff)
summary(lm1)
summary(lm2)
anova(lm1, lm2)
##The results for now did not make sense.
```
RQ1: Are there significant differences between personal
and impersonal sources in influencing individuals’ willingness to engage in the different types of connective-collective activities?
```{r, message=FALSE}
mod1 <-manova(c ~ source + attitude + involvement + internal + group_eff)
summary(mod1)
mod2 <- manova(c ~ source + elaboration)
#summary(mod2)
```

H3: Predicted that perceived source credibility will moderate source effects by being positively related to willingness to carry out the collective activities.
```{r,message=FALSE}
mod3 <- lm(action ~ source*credibility)
summary(mod3)
```

H4: Perceived source credibility will moderate the influence of
personalness of source on cognitive elaboration, such that perceived credibility is positively related to cognitive elaboration.
```{r, message=FALSE}
mod4 <- lm(elaboration ~ source*credibility)
summary(mod4)
```

*Figure 1*
```{r}
qplot(x = credibility, y = action, data = newd2, color = source) + 
  geom_smooth(method = "lm")
qplot(x = credibility, y = elaboration, data = newd2, color = source)+
  geom_smooth(method = "lm")
```


###Exploratory analyses

Any follow-up analyses desired (not required).  

## Discussion

### Summary of Replication Attempt

Open the discussion section with a paragraph summarizing the primary result from the confirmatory analysis and the assessment of whether it replicated, partially replicated, or failed to replicate the original result.  

### Commentary

Add open-ended commentary (if any) reflecting (a) insights from follow-up exploratory analysis, (b) assessment of the meaning of the replication (or not) - e.g., for a failure to replicate, are the differences between original and present study ones that definitely, plausibly, or are unlikely to have been moderators of the result, and (c) discussion of any objections or challenges raised by the current and original authors about the replication attempt.  None of these need to be long.
